---
title: 'Assignment 2: Classification for the Detection of Opinion Spam'
author: "Anouk van der Lee (6620590), Shu Zhao (6833519), Fleur Petit (5583837)"
date: "`r format(Sys.time(), '%d, %B, %Y')`"
output: 
  pdf_document:
    toc : true
---

```{r setup, include=FALSE}
library(tidyverse)
library(tm)
library(knitr)
library(kableExtra)
library(glmnet)
library(randomForest)
library(SnowballC)
library(broom)
library(NLP)
library(coefplot)
library(DT)
library(ggfortify)
library(cowplot)
library(varhandle)
library(entropy)
library(rpart)
library(rpart.plot)

knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_bw())

```

# TO DO

- Comparison of results

# 0. Pre-processing

## Load reviews

```{r prepare_df}

# Read in the data using UTF-8 encoding
reviews.false <- VCorpus(DirSource(file.path("data", "op_spam_v1.4", "negative_polarity", "deceptive_from_MTurk"), 
                                       encoding = "UTF-8",
                                       recursive = TRUE))
reviews.true <- VCorpus(DirSource(file.path("data", "op_spam_v1.4", "negative_polarity", "truthful_from_Web"), 
                                      encoding = "UTF-8",
                                      recursive = TRUE))
# Join true and false reviews into a single Corpus
reviews.all <- c(reviews.false, reviews.true)
# Create label vector
# 1 = deceptive negative, 0 = truthful negative (as deceptive negative is what we are interested in!!!)
labels <- factor(c(rep("1", length(reviews.false)), rep("0", length(reviews.true))))

```

## Prepare corpus

```{r prepare_corpus}

# Preprocess the corpus
reviews.all <- reviews.all %>%
  # Remove punctuation marks (comma’s, etc.)
  tm_map(removePunctuation) %>% 
  # Make all letters lower case
  tm_map(content_transformer(tolower)) %>% 
  # Stemming
  tm_map(stemDocument) %>%
  # Remove English stopwords
  tm_map(removeWords, stopwords("english")) %>% 
  # Remove numbers
  tm_map(removeNumbers) %>% 
  # Remove excess whitespace
  tm_map(stripWhitespace)


```

## Performance function

```{r}

performance <- function(confusion_matrix){
  tn <- confusion_matrix[1,1]
  fn <- confusion_matrix[2,1]
  n_pred <- tn+fn
  
  fp <- confusion_matrix[1,2]
  tp <- confusion_matrix[2,2]
  p_pred <- fp+tp
  
  n <- tn+fp
  p <- fn+tp
  
  performance_metrics <- tibble(metric = c("recall",
                                "miss-rate", # 1 - recall
                                "fall-out", # 1 - selectivity
                                "selectivity",
                                "prevalence",
                                "precision",
                                "false omission rate", # 1 - neg_predictive_value
                                "pos likelihood ratio",
                                "neg likelihood ratio",
                                "accuracy",
                                "false discovery rate", # 1 - precision
                                "neg predictive value",
                                "diagnostic odds ratio",
                                "F1"),
                      value = c(tp/p, # recall
                               fn/p, # 1 - recall
                               fp/n, # 1 - selectivity
                               tn/n, # selectivity
                               p/(n+p), # prevalence
                               tp/p_pred, # precision
                               fn/n_pred, # 1 - neg_predictive_value
                               (tp/p)/(fp/n), # positive likelihood ratio
                               (fn/p)/(tn/n), # negative likelihood ratio
                               (tp+tn)/(n+p), # accuracy
                               fp/p_pred, # 1 - precision
                               tn/n_pred, # negative predictive value
                               ((tp/p)/(fp/n))/((fn/p)/(tn/n)), # diagnostic odds ratio
                               2*(tp/p_pred)*(tp/p)/((tp/p_pred) + (tp/p))) # F1
  )
  
  performance_metrics
}


```

## Mutual information top n function

```{r}

# Calculate top-n high mutual-information terms' indices
calculate_topn <- function(dtm, topn) {
  # Convert document term matrix to binary (term present/absent)
  dtm.bin <- as.matrix(dtm) > 0
  
  # Compute mutual information of each term with class label
  mi <- apply(as.matrix(dtm.bin),
              2, 
              function(x,y){ mi.plugin(table(x,y)/length(y), unit="log2")},
              labels[index.train])
  
  # Sort the indices from high to low mutual information
  mi.order <- order(mi, decreasing = TRUE)
  
  # Return top-n mutual-information terms' index
  return(list(mi.order[c(1:topn)], mi[mi.order[c(1:topn)]]))
}

```

## Split in train and test data

```{r train_test_split}
# 1 fold = 80 samples
# Fold 1-4 for training = 1:320 from true + 1:320 from false
index.train <- c(c(1:320), 400+c(1:320))


## Sanity check
set <- rep("test", length(labels))
set[index.train] <- "train" 

train_test <- tibble(set = set,
                     labels = labels)

ggplot(train_test, aes(set, fill = labels)) +
  geom_bar(position = "fill")

```

### Unigrams

```{r train_test_split_uni}

# Training document-term matrix
train_dtm <- DocumentTermMatrix(reviews.all[index.train])
# Train labels
train_labels <- labels[index.train]

# Test document-term matrix
test_dtm <- DocumentTermMatrix(reviews.all[-index.train], 
                               list(dictionary = as.list(dimnames(train_dtm)[[2]])))
# Test labels
test_labels <- labels[-index.train]

```

### Bigrams

#### Functions to create bigram test dataset

```{r fun_bigram_test}
# Workaround

gen_bigram_test <- function(train_dtm, test_dtm_tmp) {
  
  # Matrix of train_dtm
  train_dtm_mat <- as.matrix(train_dtm)
  
  # Matrix of test_dtm_tmp
  test_dtm_mat_tmp <- as.matrix(test_dtm_tmp)
  
  # Final matrix of test_dtm to be returned
  test_dtm_mat <- matrix(data = NA, nrow = dim(test_dtm_mat_tmp)[1], ncol = dim(train_dtm_mat)[2])
  
  # Iterate through all the rows in the final test_dtm dataset to be filled in with 1 or 0
  for(row_index in c(1: dim(test_dtm_mat_tmp)[1])) {
    
    # Reset to the beginning of each row
    term_index <- 0
  
    # Iterate through all the terms in one row to be filled in with 1 or 0
    for(train_term in colnames(train_dtm_mat)) {
      
      # Record the term index in train_dtm2 dataset
      term_index <- term_index + 1
      
      # If the term exists in the test bigrams
      if(train_term %in% colnames(test_dtm_mat_tmp)) {
        
        # AND the term exists in the test review's comment
        if(test_dtm_mat_tmp[row_index, train_term] == 1) {
          # Label the term as 1 for existence
          test_dtm_mat[row_index, term_index] <- 1
          
          print(str_c('Current row index: ', row_index))
          print(str_c('Current term index: ', term_index))
          print(str_c('Existing term ==========> ', train_term))
          
        } else {
          
          # BUT the term does not exist in the test review's comment
          # Label the term as 0 for absence
          test_dtm_mat[row_index, term_index] <- 0
        }
        
      } else {
        # Else the term does not exist in the test bigrams
        # Label the term as 0 for absence
        test_dtm_mat[row_index, term_index] <- 0
      }
    }
  }
  
  # Set colunm names from train_dtm2 for all the terms to be matched with train_dtm2
  colnames(test_dtm_mat) <- colnames(train_dtm)
  # Set row names from test_dtm2 for all the rows to be matched with test_dtm2
  rownames(test_dtm_mat) <- rownames(test_dtm_tmp)
  
  # Return the final test bigram matrix
  return(test_dtm_mat)
}

```

#### Bigram train and test split

```{r train_test_split_bi}

# Training document-term matrix for bigrams
BigramTokenizer <- function (x) {
  unlist(lapply(ngrams(words(x), 1:2), paste, collapse = " "), use.names = FALSE)
}
    
train_dtm2 <- DocumentTermMatrix(reviews.all[index.train],
                                 control = list(tokenize = BigramTokenizer))



# Test document-term matrix for bigrams
test_dtm2_tmp <- DocumentTermMatrix(reviews.all[-index.train],
                                     control = list(tokenize = BigramTokenizer))

# Option 1: Load the existing test bigram dataset
# test_dtm2 <- read.table(file.path('data', 'test_dtm2.txt'))

# Option 2: Create the test bigram dataset
test_dtm2 <- gen_bigram_test(train_dtm2, test_dtm2_tmp)
# write.table(test_dtm2, file.path('data', 'test_dtm2.txt'))

```

#### Analysis of training and test bigrams

##### Common bigrams

```{r train_test_split_bi_analysis, eval=FALSE, include=FALSE}

train_dtm2 <- DocumentTermMatrix(reviews.all[index.train],
                                 control = list(tokenize = BigramTokenizer))

test_dtm2 <- DocumentTermMatrix(reviews.all[-index.train],
                                 control = list(tokenize = BigramTokenizer))

train_bigrams <- colnames(as.matrix(train_dtm2))

test_bigrams <- colnames(as.matrix(test_dtm2))

common_terms <- c()
index <- 0
for (test_term in test_bigrams) {
  
  index <- index + 1
  print(index)
  
  if(test_term %in% train_bigrams) {
    print(test_term)
    common_terms <- c(common_terms, test_term)
  }
}

# write.csv(data.frame(common_terms), file = file.path('data', 'common_bigrams_from_test_and_train.csv'))

```

##### Dictionary parameter

```{r dict_param, eval=FALSE, include=FALSE}

# this is the actual review from reviews.all[c(321)]
text_one_review <- read_file(file.path(file.path("data", "op_spam_v1.4", "negative_polarity", 
                                      "deceptive_from_MTurk", "fold5", "d_allegro_1.txt")))

# the bigrams which should exist!!!
dict <- c("actually asked", "bags room", "bell hop")
print("actually asked" %in% dimnames(train_dtm2)[[2]])
print("bags room" %in% dimnames(train_dtm2)[[2]])
print("bell hop" %in% dimnames(train_dtm2)[[2]])

# bigram dictionary
mat_one_review_bi <- DocumentTermMatrix(reviews.all[c(321)],
                                     list(dictionary = dict))

# bigram exist?
sum(as.matrix(mat_one_review_bi))

# unigram dictionary
mat_one_review_uni <- DocumentTermMatrix(reviews.all[c(321)],
                                     list(dictionary = c("actually", "asked")))

# unigram exist?
sum(as.matrix(mat_one_review_uni))


# double check: this is the matrix for text_one_review by printing below matrix
as.matrix(mat_one_review)

# overall test with the training vocabularies
# mat_one_review <- DocumentTermMatrix(reviews.all[c(321)],
#                                      list(dictionary = as.list(dimnames(train_dtm2)[[2]])))

```

## Get word frequency matrix

### Unigrams

```{r freq_uni}

# Remove terms that occur in less than 5% of the documents
# Training document-term matrix
train_dtm_freq <- removeSparseTerms(train_dtm, 0.95)
# Test document-term matrix
test_dtm_freq <- DocumentTermMatrix(reviews.all[-index.train], 
                                    list(dictionary = as.list(dimnames(train_dtm_freq)[[2]])))

```

### Bigrams

```{r freq_bi}

# Training document-term matrix for bigrams
train_dtm2_freq <- removeSparseTerms(train_dtm2, 0.99)

# Option 1: Load the existing test bigram dataset of frequency
# test_dtm2_freq <- read.table(file.path('data', 'test_dtm2_freq.txt'))

# Option 2: Create the test bigram dataset
test_dtm2_freq <- gen_bigram_test(train_dtm2_freq, test_dtm2_tmp)
# write.table(test_dtm2_freq, file.path('data', 'test_dtm2_freq.txt'))

```

## Get mutual information

### Unigrams

```{r mi_uni}

# Select top-n mutual-information terms from total vocabularies
index.top950 <- calculate_topn(train_dtm, topn = 950)
train_dtm_mi <- train_dtm[, index.top950[[1]]]
test_dtm_mi <- test_dtm[, index.top950[[1]]]

# Show part of mutual-info-only top-500 words
index.top950[[2]][1:30]

as.data.frame(index.top950[[2]][1:10]) %>%
  rownames_to_column("term") %>%
  rename(mutual_information = `index.top950[[2]][1:10]`) %>%
  kable()

```

### Bigrams

```{r mi_bi}

# Select top-n mutual-information bigrams from total bigrams
index.bigram.top2000 <- calculate_topn(train_dtm2, topn = 2000)
train_dtm2_mi <- train_dtm2[, index.bigram.top2000[[1]]]
test_dtm2_mi <- test_dtm2[, index.bigram.top2000[[1]]]

# Show part of mutual-info-only top-300 words
index.bigram.top2000[[2]][1:30]

as.data.frame(index.bigram.top2000[[2]][1:10]) %>%
  rownames_to_column("term") %>%
  rename(mutual_information = `index.bigram.top2000[[2]][1:10]`) %>%
  kable()

```


# 1. Multinomial naive Bayes (generative linear classifier)

## Function for multinomial Bayes classifier

```{r mnb}

# Function for multinomial naive Bayes

# Train by multinormial naive Bayes
train.mnb <- function (dtm,labels) {
  call <- match.call()
  V <- ncol(dtm)
  N <- nrow(dtm)
  prior <- table(labels)/N
  labelnames <- names(prior)
  nclass <- length(prior)
  cond.probs <- matrix(nrow=V,ncol=nclass)
  dimnames(cond.probs)[[1]] <- dimnames(dtm)[[2]]
  dimnames(cond.probs)[[2]] <- labelnames
  index <- list(length=nclass)
  for(j in 1:nclass){
    index[[j]] <- c(1:N)[labels == labelnames[j]]
  }
  
  for(i in 1:V){
    for(j in 1:nclass){
      cond.probs[i,j] <- (sum(dtm[index[[j]],i])+1)/(sum(dtm[index[[j]],])+V)
    }
  }
  list(call=call,prior=prior,cond.probs=cond.probs)    
}

# Predict by multinormial naive Bayes
predict.mnb <- function (model,dtm) {
  classlabels <- dimnames(model$cond.probs)[[2]]
  logprobs <- dtm %*% log(model$cond.probs)
  N <- nrow(dtm)
  nclass <- ncol(model$cond.probs)
  logprobs <- logprobs+matrix(nrow=N,ncol=nclass,log(model$prior),byrow=T)
  classlabels[max.col(logprobs)]
}

```

## Unigrams

### Train

#### Mutual information

```{r train_mnb_mi}

model_mnb <- train.mnb(train_dtm_mi, train_labels)

```

#### Frequency

```{r train_mnb_freq}

model_mnb_freq <- train.mnb(train_dtm_freq, train_labels)

```

### Predict

#### Mutual information

```{r predict_mnb_mi}

prediction_mnb <-  predict.mnb(model_mnb, as.matrix(test_dtm_mi))

```

#### Frequency

```{r predict_mnb_freq}

prediction_mnb_freq <-  predict.mnb(model_mnb_freq, as.matrix(test_dtm_freq))

```

### Confusion matrix

#### Mutual information

```{r conf_mnb_mi}

conf_mnb <- table(test_labels, prediction_mnb, dnn = c("actual", "predicted"))

```

#### Frequency

```{r conf_mnb_freq}

conf_mnb_freq <- table(test_labels, prediction_mnb_freq, dnn = c("actual", "predicted"))

```

### Performance metrics

#### Mutual information

```{r perf_mnb_mi}

perf_mnb <- performance(conf_mnb) 
perf_mnb %>% kable()

```

#### Frequency

```{r perf_mnb_freq}

perf_mnb_freq <- performance(conf_mnb_freq) 
perf_mnb_freq %>% kable()

```

## Bigrams

### Train

#### Mutual information

```{r train_mnb2_mi}

model_mnb2 <- train.mnb(train_dtm2_mi, train_labels)

```

#### Frequency

```{r train_mnb2_freq}

model_mnb2_freq <- train.mnb(train_dtm2_freq, train_labels)

```

### Predict

#### Mutual information

```{r predict_mnb2_mi}

prediction_mnb2 <-  predict.mnb(model_mnb2, as.matrix(test_dtm2_mi))

```

#### Frequency

```{r predict_mnb2_freq}

prediction_mnb2_freq <-  predict.mnb(model_mnb2_freq, as.matrix(test_dtm2_freq))

```

### Confusion matrix

#### Mutual information

```{r conf_mnb2_mi}

conf_mnb2 <- table(test_labels, prediction_mnb2, dnn = c("actual", "predicted"))

```

#### Frequency

```{r conf_mnb2_freq}

conf_mnb2_freq <- table(test_labels, prediction_mnb2_freq, dnn = c("actual", "predicted"))

```

### Performnace metrics

#### Mutual information

```{r perf_mnb2_mi}

perf_mnb2 <- performance(conf_mnb2) 
perf_mnb2 %>% kable()

```

#### Frequency

```{r perf_mnb2_freq}

perf_mnb2_freq <- performance(conf_mnb2_freq) 
perf_mnb2_freq %>% kable()

```

# 2. Regularised logistic regression (discriminative linear classifier)

A logistic regeression model uses the information from the document term matrix to predict the class (either '1' for deceptive or '0' for truthful). 

## Unigram

### Choose lambda

```{r cv_lasso}

# Use LASSO (penalising for number of parameters)
# Determine lambda by means of cross validation
# SHU: train_dtm -> as.matrix(train_dtm_freq)
cv_lasso <- cv.glmnet(as.matrix(train_dtm_freq), train_labels, alpha = 1, family = "binomial", type.measure="class")

lambda_uni <- plot(cv_lasso)

coefs <- as.data.frame(as.matrix(coef(cv_lasso, s="lambda.1se"))) %>%
  rownames_to_column(var = "term") %>%
  rename(coefficient = `1`) %>%
  filter(coefficient != 0)

top10coef <- coefs %>% 
  filter(term != "(Intercept)") %>% 
  arrange(desc(abs(coefficient))) %>% 
  head(10) %>%
  mutate(probability = exp(coefficient)/(exp(coefficient)+1))

top10coef %>%
  kable()


```

### Train

```{r train_glm, fig.height=10}

# SHU: train_dtm -> as.matrix(train_dtm_freq)
model_glm <- glmnet( as.matrix(train_dtm_freq), train_labels, alpha = 1, family = "binomial", 
                    lambda = cv_lasso$lambda.1se, type.measure="class") # I choose the largest lambda within 1se from the smallest lambda

coefplot(model_glm, lambda=cv_lasso$lambda.1se, sort='magnitude', cex=100)


```

### Predict

```{r predict_glm, fig.width = 10}

#test_dtm_glm <- model.matrix(test_labels ~ test_dtm)[,-1]
# SHU: test_dtm ->  as.matrix(test_dtm_freq)
predicted_glm <- predict(model_glm, 
                             newx = as.matrix(test_dtm_freq), 
                             type = "class", # Type "response" gives the fitted probabilities for "binomial"
                             s= cv_lasso$lambda.1se)


```

```{r}

# Information about hotels and wrong predictions

# wrong_reviews <- df[-train_ind,] %>%
#   filter(test_preds[["correct"]]==0)
# 
# wrong_reviews <- as.data.frame(test_dtm[test_preds[["correct"]]==0,]) %>%
#   gather(key = "word", value = "count") %>%
#   group_by(word) %>%
#   summarise(n = sum(count))
# 
# per_hotel <- df[-train_ind,] %>%
#   mutate(correct = test_preds[["correct"]]==1)
# 
# ggplot(per_hotel, aes(hotel, fill = correct)) +
#   geom_bar() + 
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### Confusion matrix

```{r confusion_glm}

test_preds <- tibble(review_type = ifelse(test_labels==1,"deceptive","truthful"),
                     prediction = ifelse(predicted_glm==1, "deceptive", "truthful"),
                     correct = ifelse(review_type == prediction, "1", "0")) %>%
  rowid_to_column("document") 

ggplot(test_preds, aes(document, prediction, colour = correct)) +
  geom_point(shape = 3, size = 4)# +
  #facet_grid(~review_type, scales = "free")

prec <- ggplot(test_preds, aes(prediction, fill = correct)) +
  geom_bar(position = "fill")

recall <- ggplot(test_preds, aes(review_type, fill = correct)) +
  geom_bar(position = "fill")

conf_glm <- table(test_labels, predicted_glm)

conf_glm

```


### Performance metrics

```{r performance_glm}

perf_glm <- performance(conf_glm)

perf_glm %>% kable()

```

## Bigram

### Choose lambda

```{r cv_lasso2}

# Use LASSO (penalising for number of parameters)
# Determine lambda by means of cross validation
# SHU: train_dtm2 -> as.matrix(train_dtm2_freq)
cv_lasso2 <- cv.glmnet(as.matrix(train_dtm2_freq), train_labels, alpha = 1, family = "binomial", type.measure = "class")

lambda_bi <-plot(cv_lasso2)

coefs2 <- as.data.frame(as.matrix(coef(cv_lasso2, s="lambda.1se"))) %>%
  rownames_to_column(var = "term") %>%
  rename(coefficient = `1`) %>%
  filter(coefficient != 0)

top10coef2 <- coefs2 %>%
  arrange(desc(abs(coefficient))) %>% 
  head(10) %>% 
  mutate(probability = exp(coefficient)/(exp(coefficient)+1)) 

top10coef2 %>%
  kable()

```

### Train

```{r train_glm2}

# SHU: train_dtm2 -> as.matrix(train_dtm2_freq)
model_glm2 <- glmnet(as.matrix(train_dtm2_freq), train_labels, alpha = 1, family = "binomial", 
                    lambda = cv_lasso2$lambda.1se) # I choose the largest lambda within 1se from the smallest lambda


```

### Predict

```{r predict_glm2}

#test_dtm_glm <- model.matrix(test_labels ~ test_dtm)[,-1]
# SHU: test_dtm2 -> as.matrix(test_dtm2_freq)

predicted_glm2 <- predict(model_glm2, 
                             newx = as.matrix(test_dtm2_freq), 
                             type = "class", # Type "response" gives the fitted probabilities for "binomial"
                             s= cv_lasso2$lambda.1se)


```

### Confusion matrix

```{r confusion_glm2}

test_preds2 <- tibble(review_type = ifelse(test_labels==1,"deceptive","truthful"),
                     prediction = ifelse(predicted_glm2==1, "deceptive", "truthful"),
                     correct = ifelse(review_type == prediction, "1", "0")) %>%
  rowid_to_column("document") 

# Shu???
#wrong_reviews <- df[-train_ind,] %>%
#  filter(test_preds2[["correct"]]==0)

ggplot(test_preds2, aes(document, prediction, colour = correct)) +
  geom_point(shape = 3, size = 4)

prec2 <- ggplot(test_preds2, aes(prediction, fill = correct)) +
  geom_bar(position = "fill")

recall2 <- ggplot(test_preds2, aes(review_type, fill = correct)) +
  geom_bar(position = "fill")

conf_glm2 <- table(test_labels, predicted_glm2)

conf_glm2 

```


### Performance metrics

```{r performance_glm2}

perf_glm2 <- performance(conf_glm2)

perf_glm2 %>% kable()

```

# Comparison logistic regression models

## Lambda plots

```{r}

tidied_cv <- tidy(cv_lasso) %>% rename(MSE = estimate)
tidied_cv2 <- tidy(cv_lasso2) %>% rename(MSE = estimate)

# plot of MSE as a function of lambda
l_cv<-ggplot(tidied_cv, aes(log(lambda), MSE)) +
  geom_point(colour = "red") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .25) +
  geom_vline(xintercept = log(cv_lasso$lambda.min)) +
  geom_vline(xintercept = log(cv_lasso$lambda.1se), lty = 2) +
  ggtitle("Unigram")

l_cv2<-ggplot(tidied_cv2, aes(log(lambda), MSE)) +
  geom_point(colour = "red") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .25) +
  geom_vline(xintercept = log(cv_lasso$lambda.min)) +
  geom_vline(xintercept = log(cv_lasso$lambda.1se), lty = 2) +
  ggtitle("Bigram")

ggsave(plot_grid(l_cv, l_cv2), filename = "cv_lambda.png", width = 9, height = 3)

```

## Coefficient tables

```{r}

top10coef %>% kable()

top10coef2 %>% kable() 

```

## Confusion matrix plots

```{r}

ggsave(plot_grid(prec + theme(legend.position = "none"), 
                 recall + theme(legend.position = "none"), 
                 prec2, recall2), 
       filename = "conf_plots.png", height = 4)

```

## Performance

```{r}

compare_glms <- tibble(metric = perf_mnb[["metric"]],
                       glm = perf_glm[["value"]],
                       glm2 = perf_glm2[["value"]]) %>%
  filter(metric %in% c("precision", "neg predictive value", "recall", "selectivity", "accuracy"))

compare_glms %>% kable()


```


# 3. Classification trees (flexible classifier)

## Unigrams

### Train

#### Mutual information

```{r train_tree_mi}

# hyper-parameter: feature selection
cp.rpart <- 0.036
minsplit.rpart <- 15
minbucket.rpart <-5
loss.rpart <- matrix(c(0, 1, 2, 0), nrow = 2, ncol = 2, byrow = TRUE)

model_tree <- rpart(label ~ ., 
                  data = data.frame(as.matrix(train_dtm_mi), 
                                             label = train_labels), 
                  cp = cp.rpart,
                  minsplit = minsplit.rpart,
                  minbucket = minbucket.rpart,
                  parms = list(loss = loss.rpart),
                  method = "class")

```

#### Frequency

```{r train_tree_freq}

# hyper-parameter: feature selection
cp.rpart <- 0.036
minsplit.rpart <- 15
minbucket.rpart <-5
loss.rpart <- matrix(c(0, 1, 2, 0), nrow = 2, ncol = 2, byrow = TRUE)

model_tree_freq <- rpart(label ~ ., 
                  data = data.frame(as.matrix(train_dtm_freq), 
                                             label = train_labels), 
                  cp = cp.rpart,
                  minsplit = minsplit.rpart,
                  minbucket = minbucket.rpart,
                  parms = list(loss = loss.rpart),
                  method = "class")

```

### Predict

#### Mutual information

```{r predict_tree_mi}

prediction_tree <- predict(model_tree,
                           newdata = data.frame(as.matrix(test_dtm_mi)),
                           type = "class")
```

#### Frequency

```{r predict_tree_freq}

prediction_tree_freq <- predict(model_tree_freq,
                           newdata = data.frame(as.matrix(test_dtm_freq)),
                           type = "class")
```

### Confusion matrix 

#### Mutual information

```{r conf_tree_mi}

conf_tree <- table(test_labels, prediction_tree, dnn = c("actual", "predicted"))

```

#### Frequency

```{r conf_tree_freq}

conf_tree_freq <- table(test_labels, prediction_tree_freq, dnn = c("actual", "predicted"))

```

### Performance metrics

#### Mutual information

```{r performance_tree_mi}

perf_tree <- performance(conf_tree)
perf_tree %>% kable()

```

#### Frequency

```{r performance_tree_freq}

perf_tree_freq <- performance(conf_tree_freq)
perf_tree_freq %>% kable()

```

## Bigrams

### Train

#### Mutual information

```{r train_tree2_mi}

cp.rpart.bigram <- 0
minsplit.rpart.bigram <- 15
minbucket.rpart.bigram <- 5
loss.rpart.bigram <- matrix(c(0, 1, 2, 0), nrow = 2, ncol = 2, byrow = TRUE)

model_tree2 <- rpart(label ~ ., 
                  data = data.frame(as.matrix(train_dtm2_mi), 
                                             label = train_labels), 
                  cp = cp.rpart.bigram,
                  minsplit = minsplit.rpart.bigram,
                  minbucket = minbucket.rpart.bigram,
                  parms = list(loss = loss.rpart.bigram),
                  method = "class")

```

#### Frequency

```{r train_tree2_freq}

cp.rpart.bigram <- 0
minsplit.rpart.bigram <- 15
minbucket.rpart.bigram <- 5
loss.rpart.bigram <- matrix(c(0, 1, 2, 0), nrow = 2, ncol = 2, byrow = TRUE)

model_tree2_freq <- rpart(label ~ ., 
                  data = data.frame(as.matrix(train_dtm2_freq), 
                                             label = train_labels), 
                  cp = cp.rpart.bigram,
                  minsplit = minsplit.rpart.bigram,
                  minbucket = minbucket.rpart.bigram,
                  parms = list(loss = loss.rpart.bigram),
                  method = "class")

```

### Predict

#### Mutual information

```{r predict_tree2_mi}

prediction_tree2 <- predict(model_tree2,
                           newdata = data.frame(as.matrix(test_dtm2_mi)),
                           type = "class")

```

#### Frequency

```{r predict_tree2_freq}

prediction_tree2_freq <- predict(model_tree2_freq,
                           newdata = data.frame(as.matrix(test_dtm2_freq)),
                           type = "class")

```

### Confusion matrix 

#### Mutual information

```{r conf_tree2_mi}

conf_tree2 <- table(test_labels, prediction_tree2, dnn = c("actual", "predicted"))

```

#### Frequency

```{r conf_tree2_freq}

conf_tree2_freq <- table(test_labels, prediction_tree2_freq, dnn = c("actual", "predicted"))

```

### Performance metrics

#### Mutual information

```{r perf_tree2_mi}

perf_tree2 <- performance(conf_tree2)
perf_tree2 %>% kable()

```

#### Frequency

```{r perf_tree2_freq}

perf_tree2_freq <- performance(conf_tree2_freq)
perf_tree2_freq %>% kable()

```


# 4. Random forests (flexible classifier)

##unigram

###select mtry value

```{r}
#select different values using the method described in the report
ntreeTry = 100
stepFactor = 5.12
improve = 0.001

mtry = 9


#run and notate results
# SHU: train_dtm -> as.matrix(train_dtm_freq)
model_random <- tuneRF (x = as.matrix(train_dtm_freq), y = train_labels, mtry = mtry, ntreeTry = ntreeTry, stepFactor = stepFactor, improve= improve, trace = TRUE, plot = TRUE, doBest = FALSE)

```

###select nodesize
```{r}
nodelist <- c()

#check if mtry is indeed the chosen mtry
mtry = 9
ntreeTry = 50

#select a range for i for minimal size of terminal nodes
# SHU: train_dtm -> as.matrix(train_dtm_freq)
for (i in 1: 1000){
  model_random <- randomForest(x = as.matrix(train_dtm_freq), y = train_labels, mtry = mtry, nodesize = i, ntree = ntreeTry, importance = TRUE, do.trace = FALSE)
  
  #select the out of bag score after all trees have run 
  nodelist <- c(nodelist, model_random$err.rate[ntreeTry,1])
  print(i)
  print(model_random$err.rate[ntreeTry,1])
}

nodelist

#Create a plot of the data gathered
nodeplot <- tibble(OOB = nodelist) %>%
  rowid_to_column("nodesize") %>%
  ggplot(aes(nodesize, OOB)) +
  geom_point() +
  geom_line()

nodeplot


#now select the best nodesize value
```


###train

```{r}
#Check if nodesize is indeed the chosen nodesize
nodesize = 63
ntreeTry = 2000

#Train the model with the chosen values on the unigram dataset
# SHU: train_dtm -> as.matrix(train_dtm_freq)
model_random <- randomForest(x = as.matrix(train_dtm_freq), y = train_labels, mtry = mtry, nodesize = nodesize, ntree = ntreeTry, importance = TRUE, do.trace = TRUE)


```


### Predict

```{r predict_random}

predicted_random <- predict(model_random, test_dtm, type = "response")

```

### Confusion matrix 

```{r conf_random}

conf_random <- table(test_labels, predicted_random)
conf_random

```

### Performance metrics

```{r performance_random}

perf_random <- performance(conf_random)
perf_random %>% kable()

```


##bigram
###select mtry value

```{r}


#select different values using the method described in the report
ntreeTry2 = 100
stepFactor2 = 33.34
improve2 = 0.001
mtry2 = 3


#run and notate results
#SHU: train_dtm2 -> as.matrix(train_dtm2_freq)
model_random2 <- tuneRF (x = as.matrix(train_dtm2_freq), y = train_labels, mtry = mtry2, ntreeTry = ntreeTry2, stepFactor = stepFactor2, improve= improve2, trace = TRUE, plot = TRUE, doBest = FALSE)

```

###select nodesize
```{r}
nodelist2 <- c()

#check if mtry is indeed the chosen mtry
mtry2 = 3
ntreeTry2 = 20

#select a range for i for minimal size of terminal nodes
#SHU: train_dtm2 -> as.matrix(train_dtm2_freq)
for (i in 1: 1000){
  model_random2 <- randomForest(x = as.matrix(train_dtm2_freq), y = train_labels, mtry = mtry2, nodesize = i, ntree = ntreeTry2, importance = TRUE, do.trace = FALSE)
  
  #select the out of bag score after all trees have run 
  
  nodelist2 <- c(nodelist2, model_random2$err.rate[ntreeTry2,1])
  print(i)
  print(model_random2$err.rate[ntreeTry2,1])
}

nodelist2

#Create a plot of the data gathered
nodeplot2 <- tibble(OOB = nodelist2) %>%
  rowid_to_column("nodesize") %>%
  ggplot(aes(nodesize, OOB)) +
  geom_point() +
  geom_line()

nodeplot2


#now choose a value for nodesize by hand
```


###train

```{r}
#Check if nodesize is indeed the chosen nodesize
nodesize2 = 125 
ntreeTry2 = 100

#Train the model with the chosen values on the unigram dataset
#SHU: train_dtm2 -> as.matrix(train_dtm2_freq)
model_random2 <- randomForest(x = as.matrix(train_dtm2_freq), y = train_labels, mtry = mtry2, nodesize = nodesize2, ntree = ntreeTry2, importance = TRUE, do.trace = TRUE, keep.forest = TRUE)


```


### Predict

```{r predict_random}

predicted_random2 <- predict(model_random2, test_dtm2, type = "response")

```

### Confusion matrix 

```{r conf_random}

conf_random <- table(test_labels, predicted_random2)
conf_random

```

### Performance metrics

```{r performance_random}

perf_random <- performance(conf_random)
perf_random %>% kable()

```


# Comparison

## Performance metrics

```{r perf_compare}

perf_compare <- tibble(metric = perf_mnb[["metric"]],
                       mnb = perf_mnb[["value"]],
                       glm = perf_glm[["value"]],
                       glm2 = perf_glm2[["value"]],
                       tree = perf_tree[["value"]],
                       random = perf_random[["value"]])

perf_compare %>% kable()


```

## Logistic regression


```{r}

predictions_per_model <- tibble(predictions = c(predicted_mnb, 
                                      as.vector(predicted_glm), 
                                      predicted_tree,
                                      predicted_random),
                      models = c(rep("mnb", 
                                     length(predicted_mnb)), 
                                 rep("logistic regression", 
                                     nrow(predicted_glm)), 
                                 rep("single tree", 
                                     length(predicted_tree)),
                                 rep("random forest",
                                     length(predicted_random))), 
                      ground_truth = c(rep(test_labels, 4)), 
                      correct = ifelse(ground_truth == predictions, 1, 0)) %>%
  mutate(models = factor(models,levels=c("mnb", "logistic regression", "single tree", "random forest")))


glm(correct ~ models, family = "binomial", data = predictions_per_model) %>% 
  tidy() %>%
  kable()


```
